---
title: ""
date: "`r Sys.Date()`"
output:
  pdf_document:
  rmdformats::readthedown:
    highlight: kate
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```


```{r include=FALSE}


#

require(xts)
require(TTR)
require(roll)
# set wd
homedir<- "/Users/Eric/Documents/IFUND_comp"
datadir<- "/Users/Eric/Documents/IFUND_comp/data"
setwd(homedir)

load("U_train.RData")
load("U_test.RData")


##
betaExposure<- function(portf, UniverseBeta){ # portf: list; UniverseBeta: df
  tmp<- as.data.frame(unlist(portf, use.names = T))
  colnames(tmp)<- 'weight'
  tmp<- merge( tmp, UniverseBeta, by= 0, all.x=T)
  return(sum(tmp$weight* tmp$Beta, na.rm=T))
  
  
}


portfConst<- function( UniverseNames, weights){
  res<- list()
  for ( c in UniverseNames){
    if( c %in% names(weights)) {
      res[[c]]<- as.numeric(weights[c])
    }else  res[[c]]<-0
  }
  
  return(res)
  
}

portfRet<- function( Universe, portf, betahedge= F, INDX, UniverseBeta){ # Universe: list; portf: list
  tmp<- list()
  for ( x in names(Universe)){
    tmp[[x]]<- Universe[[x]]$RET.CC.1 * portf[[x]]
  }
  tmp<- as.data.frame(tmp)
  tmp<- apply(tmp, 1, sum)
  tmp<- xts(tmp, order.by = as.Date(index(Universe[[1]])))
  if( betahedge){
    beta<- betaExposure(portf, UniverseBeta)
    tmp<- tmp- beta* INDX$RET.CC.1
    
  }
  
  return(tmp)
  
}

ret2value<- function(ret){ # ret: xts
  value<- rep(0, length(ret))
  tmp<-1
  for (i in 1: length(value)){
    if(! is.na(ret[i])){
      value[i]<- tmp* (1+ ret[i])
    }else{
      value[i]<- tmp
    }
    tmp<- value[i]
    
  }
  return(xts(value, order.by = as.Date(index(ret))))
}


## work over liquid Universal (in sample daily AMOUT median > 5e5)

tmp<- sapply(U_train, function(x) median(x$AMOUNT))> 5e5
U_train_liq<- U_train[tmp]
liq_name<- names(U_train_liq)
U_test_liq<- U_test[liq_name]



U_train_liq.Vol.1<- data.frame(unlist(lapply(U_train_liq, function(x) sd(x$RET.CC.1, na.rm = T)), use.names = T))
colnames(U_train_liq.Vol.1)<- "Vol"
U_train_liq.iVol.1<- as.data.frame(unlist(lapply(U_train_liq, function(x) sd(x$RET.CO.1, na.rm = T)), use.names = T))
colnames(U_train_liq.iVol.1)<- "iVol"
U_train_liq.oVol.1<- as.data.frame(unlist(lapply(U_train_liq, function(x) sd(x$RET.OC.1, na.rm = T)), use.names = T))
colnames(U_train_liq.oVol.1)<- "oVol"
U_train_liq.ioCor.1<-as.data.frame(unlist( lapply(U_train_liq, function(x) as.numeric(cor(x$RET.CO.1, x$RET.OC.1, method = "spearman", use= "complete.obs"))), use.names = T))
colnames(U_train_liq.ioCor.1)<- "ioCor"

UTrainLiqVol<- cbind(U_train_liq.iVol.1,
                     U_train_liq.oVol.1,
                     U_train_liq.Vol.1,
                     U_train_liq.ioCor.1)
UTrainLiqVol$Names<- as.character(rownames(UTrainLiqVol))
UTrainLiqVolPtle<-as.data.frame( apply( UTrainLiqVol, 2, FUN = function(x) rank(as.numeric(x))/ (dim(UTrainLiqVol)[1])))
UTrainLiqVolPtle$Names<- UTrainLiqVol$Names
rownames(UTrainLiqVolPtle)<- rownames(UTrainLiqVol)

# overnight and intrday vol contribution




flag1<- UTrainLiqVolPtle$Vol< 0.25
flag2<- UTrainLiqVolPtle$Vol> 0.75 #& UTrainLiqVolPtle$Vol< 0.8


flag1Names<- as.character(UTrainLiqVolPtle[flag1, ]$Names)
flag2Names<- as.character(UTrainLiqVolPtle[flag2, ]$Names)
a<- rep(1/ length(flag1Names), length(flag1Names))
names(a)<- flag1Names
b<- rep(1/ length(flag2Names), length(flag2Names))
names(b)<- flag2Names
w<- a



# # low vol and high vol
# U_train_liq_IO$lowVolFlag<- U_train_liq_IO$U_train_liq.Vol.1.orderPct< 0.25
# U_train_liq_IO$highVolFlag<- U_train_liq_IO$U_train_liq.Vol.1.orderPct>0.75
# 
# lvNames<- U_train_liq_IO[U_train_liq_IO$lowVolFlag, ]$Names
# hvNames<- U_train_liq_IO[U_train_liq_IO$highVolFlag,]$Names
# lvWeights<- rep(1/ length(lvNames), length(lvNames))
# names(lvWeights)<- as.character(lvNames)
# hvWeights<- -rep(1/ length(hvNames), length(hvNames))
# names(hvWeights)<- as.character(hvNames)
# 
# 
# 
# a<- U_train_liq_IO$U_train_liq.oVol.1.orderPct< 0.25 & U_train_liq_IO$U_train_liq.Vol.1.orderPct<0.5
# b<- U_train_liq_IO$U_train_liq.oVol.1.orderPct>0.75 &  U_train_liq_IO$U_train_liq.Vol.1.orderPct>0.5
# 
# longNames<- as.character(U_train_liq_IO[a, ]$Names)
# shortNames<- as.character(U_train_liq_IO[b,]$Names)
# longs<- rep(1/ length(longNames), length(longNames))
# shorts<- rep(-1/length(shortNames), length(shortNames))
# names(longs)<- longNames
# names(shorts)<- shortNames
# 
# 

## test 
## 


load( "INDX_EQW.RData")
INDX_EQW$AMOUNT_ema15<- EMA(INDX_EQW$AMOUNT, n = 15)
INDX_EQW$AMOUNT_ema60<- EMA(INDX_EQW$AMOUNT, n= 60)
INDX_EQW$AMOUNT_ema15g60<- ifelse( INDX_EQW$AMOUNT_ema15> INDX_EQW$AMOUNT_ema60, 1, -1)



INDX_EQW$VALUE<- ret2value(INDX_EQW$RET.CC.1)
INDX_EQW$VOLUME<- INDX_EQW$AMOUNT/ INDX_EQW$VALUE
INDX_EQW$sd50<- runSD(x = INDX_EQW$RET.CC.1, n = 50)
INDX_EQW$signedlogVolume<- log(INDX_EQW$VOLUME)* sign(INDX_EQW$RET.CC.1)
INDX_EQW$signedsd50<- INDX_EQW$sd50* sign(INDX_EQW$RET.CC.1)
INDX_EQW$signedsd50logVolume<- INDX_EQW$sd50* INDX_EQW$signedlogVolume
INDX_EQW$lag5signedlogVolume<- lag(INDX_EQW$signedlogVolume, k = 5)
INDX_EQW$lag10signedlogVolume<- lag(INDX_EQW$signedlogVolume, k=10)
INDX_EQW$ma30signedlogVolume<- runMean(INDX_EQW$signedlogVolume, n = 30)
INDX_EQW$lag5ma30signedlogVolume<- lag(INDX_EQW$ma30signedlogVolume, k = 5)
INDX_EQW$lag5signedsd50<- lag(INDX_EQW$signedsd50, k = 5)


split_flag= as.Date('2016-01-01')
INDX_EQW_train<- INDX_EQW[ index(INDX_EQW)<  split_flag, ]
INDX_EQW_test<- INDX_EQW[index(INDX_EQW)>  split_flag, ]

UTrainLiqBeta<- as.data.frame(unlist( lapply(U_train_liq, FUN= function(x) as.numeric(lm(x$RET.CC.1~ INDX_EQW_train$RET.CC.1)$coef[2] )), use.names = T))
colnames(UTrainLiqBeta)<- "Beta"

portf_a<- portfConst( UniverseNames = names(U_train_liq), a)
portfBeta_a<- betaExposure(portf_a, UTrainLiqBeta)

portfret_a<- portfRet(Universe = U_test_liq, portf = portf_a, betahedge = T, INDX = INDX_EQW_test, UniverseBeta = UTrainLiqBeta )
portfValue_a<- ret2value(portfret_a)
summary(portfret_a)
plot(portfValue_a)


portf_b<- portfConst( UniverseNames = names(U_train_liq), b)
portfBeta_b<- betaExposure(portf_b, UTrainLiqBeta)

portfret_b<- portfRet(Universe = U_test_liq, portf = portf_b, betahedge = T, INDX = INDX_EQW_test, UniverseBeta = UTrainLiqBeta )
portfValue_b<- ret2value(portfret_b)
summary(portfret_b)
plot(portfValue_b)



tmp.1<- cbind( INDX_EQW_test$AMOUNT_ema15g60, portfret_a, portfret_b)
colnames(tmp.1)<- c("flag", "portfret_a", 'portfret_b')
tmp.1$portfret_c<- as.numeric(apply( tmp.1, 1, function(x) ifelse(is.na(x[1]), NA, ifelse(x[1]>0 , x[3], x[2] ))))

portfret_c<- tmp.1$portfret_c
summary(tmp.1)

plot(ret2value(portfret_c))
plot(ret2value(INDX_EQW_test$RET.CC.1))

portf_d<- portfConst(UniverseNames = names(U_train_liq), c(a, -b))
portfret_d<- portfRet(Universe =  U_train_liq, portf = portf_d, betahedge = T, INDX = INDX_EQW_train, UniverseBeta = UTrainLiqBeta)




```



# Volatility Factor In China Euqity Market

## A simple portfolio 
### Data
All stocks(3000+) listed in China A share mkt on 2016-12-30. Each has OHLC and `Volume` and `Amount` (Cash Volume).


### Universe

We thinning the world.

Criteria: 

1. Select stocks that have full history (traded from 2014-01-01 to 2016-12-30) 

+ Then there are (2400+ ) stocks remaining. We build a mkt equal weight index `INDX_EQW` at this level, and use it as hedge if any.

2. Cut the whole database into _train_ and _test_. 

+ _train_: 2014-01-01 -- 2015-12-31
+ _test_ : 2016-01-01 -- 2016-12-30

3. We play over the liquid world. Based on the _train_ dataset, screen out stocks that have median of daily `AMOUNT` less than half billion CNY. 

__Now there are 104 stocks remaining. Welcome to the liquid playgroud! __

### Assumption 

Volatility has positive return over US/EURO equity market. One explanation is that institutions prefer low vol stock due to tight risk budget. So a _long low vol/short high vol_ portfolio has unexplained (by mkt) positive return. 

__Does it apply to China Equity Mkt? __


### Portfolio

Due to the short ban, it is hard to short single stocks. The portfolio implements the long and hedge out mkt beta by `INDX_EQW`

__Portfolio P1__:

+ long: stocks in the first quartile of return std deviation (computation bases on _train_ dataset)
+ short: stocks in the last quartile of return std deviation
+ hedge: neutralize the mkt beta by `INDX_EQW` (beta estimation is based on _train_ dataset)


The _long _ names and weights  (equal weight): 

``` {r echo=T}
w<- c(a, -b)
print(w)

```

Beta of _long_ and _short_:

```{r echo =T}

portf_a<- portfConst( UniverseNames = names(U_train_liq), a)
portfBeta_a<- betaExposure(portf_a, UTrainLiqBeta)

print(portfBeta_a)

portf_b<- portfConst( UniverseNames = names(U_train_liq), b)
portfBeta_b<- betaExposure(portf_b, UTrainLiqBeta)

print(portfBeta_b)


```

One can neutralize the beta by `INDX_EQW`


### Performance

For stake of simplicity, we hold staic portfilio. 

The in-sample performance. 

```{r echo=T}

portf_d<- portfConst( UniverseNames = names(U_train_liq), w)
portfBeta_d<- betaExposure(portf_d, UTrainLiqBeta)

portfret_d<- portfRet(Universe = U_train_liq, portf = portf_d, betahedge = T, INDX = INDX_EQW_train, UniverseBeta = UTrainLiqBeta )
portfValue_d<- ret2value(portfret_d)
summary(portfret_d)

plot(ret2value(portfret_d))
plot(INDX_EQW_train$VALUE)
```



P1 fails to match the index, especially in the period 2014-11 -- 2015- 07. Timing is necessary.


## Volatility and Risk Appetite 

As metioned above, volatility facotr return comes from risk aversion. But the mkt is not always risk averse. Timing should be applied. 

#### Intuition

_When the mkt is a safe heaven, investors loosens risk budget and tends to play risk. Then low vol premium (low vol/high vol portfolio return) is negative. _

_When the mkt is tight, safety, ie low volatility, has highest priority. _

## Volatility: Timing is the Key

#### Vol Timing Factor: Amount/Volume and Volatility

Intuition indicates 2 factors: Volume and Volatility 

Note: 

1. The dataset doesnot have a mktwise volume entry. I use the `INDX_EQW` hypothetical volume (AMOUNT/VALUE) instead.

2. Chinese mkt does not have an indicator like `VIX`. The proxy I use is `INDX_EQW` 50d rolling std div. 

```{r echo= T}
lm.1<- lm(portfret_d~ INDX_EQW_train$RET.CC.1+ log(INDX_EQW_train$VOLUME)+ INDX_EQW_train$sd50)

summary(lm.1)

```

Seems like the hedge is effective. `RET.CC.1` is not relevant to the low vol premium. 


__IDEA:  Volume and Volatility should have double effect-- explosion can happen both when mkt is overheaded or in panic-- so direction should be introduced.__


``` {r echo= T}

lm.2<- lm(portfret_d~ INDX_EQW_train$signedlogVolume+ INDX_EQW_train$sd50)

summary(lm.2)

```

Here is the magic

``` {r echo= T}

lm.3<- lm(portfret_d~ INDX_EQW_train$signedlogVolume+ INDX_EQW_train$signedsd50+ INDX_EQW_train$signedsd50logVolume)

summary(lm.3)

```

Seems like `signedVolume` dominates.

Here is the majestic: 


``` {r echo= T}

lm.4<- lm(portfret_d~ INDX_EQW_train$signedlogVolume+ INDX_EQW_train$ma30signedlogVolume+ INDX_EQW_train$signedsd50)

summary(lm.4)

cor(cbind(INDX_EQW_train$signedlogVolume, INDX_EQW_train$ma30signedlogVolume, INDX_EQW_train$signedsd50), use= 'complete.obs')


lm.4<- lm(portfret_d~ INDX_EQW_train$signedlogVolume+ INDX_EQW_train$ma30signedlogVolume+ INDX_EQW_train$sd50)

summary(lm.4)

cor(cbind(INDX_EQW_train$signedlogVolume, INDX_EQW_train$ma30signedlogVolume, INDX_EQW_train$sd50), use= 'complete.obs')

```


Consider the lag version: 

``` {r echo= T}

lm.5<- lm(portfret_d~ INDX_EQW_train$lag5signedlogVolume+  INDX_EQW_train$lag5ma30signedlogVolume)

summary(lm.5)

cor(INDX_EQW_train$lag5signedlogVolume, INDX_EQW_train$lag5ma30signedlogVolume, use= 'complete.obs')
```


_Conclusion:_

_Low Vol premium is highly related to `signedlogVolume` and `signedsd50`, even with respect to the lag of moving average smoothed version._

#### More to Go

Other Potential Factors: 

Limit-up Ceiling

Limit-down Floor

Intraday Floor-Ceiling dynamics

Implied Vol forecasting (China VIX)

......



#### The Full Model 


Just as many other factors, the factor return of low vol depends over the market regime. One systametic approach to dynamic factor rotation strategies  is a _Market Regime Switch Model_. 


##### Market Regime Switch: Probablity Graphic Approach

Markov Graph: Different Market status, Status may transfer. The transition is described by a transition matrix. One optimal factor portfolio should be held if one does not have a forecasting power to the forward mkt status. The optimal factor portfolio can be a start point of a multi factor rotation strategy. 


##### Some adhoc ways

ML approach: SVM classification. RF ?? 



## Way to Go

The problems: 

1. Beta estimation

Dynamic beta hedge is not employed. The portfolio does have beta exposure though not significant. 


2. Vol estimtion

Intuitively, Volatility should have extra info to the vol premium. An accurate estimation and forecasting of mkt realized vol may help (For how, check  http://rpubs.com/ericwbzhang/217044 ) 

Some info from the implied vol may boost portfolio performance. 

3. More signal introduced to forecast vol premium.  

eg. Celling and Floor.

4. The Full Modell: Market Regime Switch 


5. The Value of PM

Factor is employed by many professional investors since it is understandable, which means forecastable for seasoned practioners. PMs with alpha should have a forecasting power over the forward mkt status. The role a quant may play is to reveal what happens in a clear way. 


## Show-off

I dont have much time to do a bar-by-bar out of sample backtesting. (Note that what I have done is purely over 2014-2015 dataset, the 2016 test set is not touched. ) While a quick guess may be good enough.



```{r echo= T}
plot(INDX_EQW_test$VALUE)

plot(INDX_EQW_test$sd50)

plot(INDX_EQW_test$VOLUME)
plot(INDX_EQW_train$VOLUME)

```


__Recall `lm.4`: Vol premium is positive when mkt is weak and mild, ie. the bar is short and volmue is gradually expanding-- this is what happens during 2016.__

__One could make a guess that the vol premium during 2016 should be decent (different from the trivial performance in 2014-2015), and the beginning may suffer a mild drawdown. __

See what actually happens: 

``` {r echo=T}

portf_e<- portfConst(UniverseNames = names(U_train_liq), c(a, -b))
portfret_e<- portfRet(Universe =  U_test_liq, portf = portf_e, betahedge = T, INDX = INDX_EQW_test, UniverseBeta = UTrainLiqBeta)

portfValue_e<- ret2value(portfret_e)

plot(portfValue_e)

summary(portfret_e)


# Sharpe Ratio
mean(portfret_e, na.rm=T)/ sd(portfret_e, na.rm = T)*16




```


